---
title: "Introduction to the dspace package"
author: Adam Dąbrowski, Jakub Nowosad
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction-to-the-dspace-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dspace)
```

Dspace (divide space) is designed for spatial segmentation/clustering/regionalization of **point or polygon data of class 'sf'**. It uses igraph to build a topological network/graph connecting points or polygons centroids. The nodes of the graph are connected with their nearest neighbours based on defined criteria (eg. nearest neighbours or queen/rook neighbourhood - see...) and the wieght of the edge is calculated as similarity between two nodes. To find network communities which represent regions/spatial clusters/submaretes it uses fast greedy algorithm (add citation) .

This package has been developed mainly for **real estate market segmentation (submarket delimitation)** but can be easily adapted to any variety of spatial data.

The package uses following functions:

 * points_ds - which devides point data into spatially coherent regions,
 * polygons_ds - which devides polygon data into spatially coherent regions,
 * find_no_clusters - which analyzes a range of divisions (by default from 2 to 30 regions) to find the one with highest modularity value (add citation)
 * plot_modularity - which visualizes the result of find_no_clusters to find the best number of clusters to divide your data

#Where to start
```
data(realEstate)
realEstate.modularity <- regionalize(realEstate, polygon = FALSE)
plot_modularity(realEstate.modularity)
realEstate$class <- points_ds(realEstate, k = 5, accuracy = FALSE)
```
